---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# chromascope

<!-- badges: start -->
<!-- badges: end -->

The goal of chromascope is to explore colours() and find interesting set of colours.

## Installation

You can install the development version of chromascope like so:

```{r, eval = FALSE}
# install.packages('devtools')
devtools::install_github('njtierney/chromascope')

```


## Example

chromascope provides functions to extract colour data from colours().

```{r example}
library(chromascope)

```


```{r}
# Extract the hex code for the colour "red"
col2hex("red")

```

```{r}
# Extract the hue, chroma, and luminance (hcl) data for the colour "red"
col2hcl("red")

```

```{r}
# Extract the red, green, and blue (rgb) data for the colour "red"
col2rgb("red")
```

```{r}
# Extract the hex code, hcl and rgb data for the colour "red".
colour_data("red")
```

## Example for vectors of colours

chromascope can work with vectors as well.

```{r}
set.seed(19-11-2025)
random_cols <- sample(colours(), 10)

```

```{r}
col2hex(random_cols)
```

```{r}
col2rgb(random_cols)
```

```{r}
col2hcl(random_cols)
```

```{r}
colour_data(random_cols)
```

## Visualise the colours on specplot() and swatchplot()

```{r}
library(colorspace)

random_cols <- colour_data(random_cols)

swatchplot(random_cols$name)



```


```{r}
specplot(random_cols$hex)
```

```{r}
# Arrange the random colours based on the hue and visualise using specplot()
library(dplyr)

random_cols |>
  arrange(luminance) |>
  pull(hex) |>
  specplot()

random_cols |>
  arrange(chroma) |>
  pull(hex) |>
  specplot()

random_cols |>
  arrange(hue) |>
  pull(hex) |>
  specplot()


```


# Find nearest R colours

```{r}
library(colorspace)
qual_cols <- qualitative_hcl(7)
qual_cols
swatchplot(qual_cols)
near_qual_cols <- nearest_colour(qual_cols)
near_qual_cols

library(dplyr)

near_qual_cols |> 
  pull(hex_base) |> 
  swatchplot(qual_cols)

near_qual_cols |> 
  pull(hex_base) |> 
  specplot(qual_cols)

```

